Summer 2024 Report

### 2024-11-14 Relations/Report.tex
Theorem 1.2.3 progress

>>>>

\subsection{Recurrence property and increasing relations}

In [TeReSe], a relation $R \sse A \times A$ is called \emph{increasing} if there
exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $x, y \in A$,
 \[ Rxy \to |x| < |y| \]

\begin{prop}
  If $R$ is increasing, then no infinite $R$-increasing sequence is bounded.
\end{prop}
\begin{proof}
  Let $(a_i) = a_0 \to a_1 \to a_2 \to \cdots$ be an $R$-increasing sequence
  and suppose that $(a_i)$ is bounded.  Let $b$ be the bound, so that $a_i \to b$ for all $i$.

  If $m = |b|$ then we have
  \[ 0 \le |a_0| < |a_1| < |a_2| < \cdots < |a_m| < |b| = m \]
  % \[ m > |a_m| > |a_{m-1}| > \cdots > |a_0| \ge 0 \]
  which is a contradiction, since there are only $m-1$ integers strictly less than $m$.
\end{proof}

It follows that every relation that is increasing in the sense of [TeReSe]
vacuously satisfies the RP condition.

\begin{cor}
  If $R$ is increasing, then $R$ has the recurrence property.
\end{cor}
